\documentclass[12pt, reqno]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amsfonts, amssymb, amsthm, setspace, hyperref}
\numberwithin{equation}{section}
\parindent 0mm
\onehalfspacing
\addtolength{\textwidth}{2 truecm}
\setlength{\hoffset}{-1 truecm}

\newcommand{\e}{\epsilon}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\w}{\omega}
\let\oldemptyset\emptyset
\let\emptyset\varnothing

\newcommand{\intersect}{\bigcap}
\newcommand{\union}{\bigcup}
\newcommand{\disjointunion}{\coprod} 
\newcommand{\powerset}{\mathcal{P}}
\newcommand{\dist}{\sim}
\renewcommand{\P}{P}
\newcommand{\E}{\text{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\given}{\mid}
\newcommand{\innerproduct}[2]{\left\langle{ #1, #2 }\right\rangle}

\begin{document}

\title{Casella and Berger Notes and Exercises -  Chapter 4}
\author{Austin David Brown}
\maketitle

\section*{Exercises}

Using this problem set:
http://www.stat.ufl.edu/~jhobert/sta6326

Chapter 4: 1, 2, 4, 9, 10, 11, 15, 19(a), 22, 23, 24, 26, 27

Chapter 4: 30, 31, 33, 35, 39, 41, 45, 47, 51, 53, 55, 64

{\bf (4.1)\rule{\textwidth}{.5pt}}

Straight forward.

{\bf (4.2)\rule{\textwidth}{.5pt}}

These all follow directly from properties of the integral.

{\bf (4.4)\rule{\textwidth}{.5pt}}

Integrating over a rectangle but the density is a the perimeter. Kind of odd, but pretty straight forward.

{\bf (4.9)\rule{\textwidth}{.5pt}}

Couple ways to do this, but pretty straight forward.

{\bf (4.10)\rule{\textwidth}{.5pt}}

Straight forward.

{\bf (4.11)\rule{\textwidth}{.5pt}}

Read the problem wrong. If you read it right, it is fairly obvious.

{\bf (4.15)\rule{\textwidth}{.5pt}}

REDO I really made a mess of this one.

{\bf (4.19)\rule{\textwidth}{.5pt}}

REDO I missed the easy way to do this.

{\bf (4.22)\rule{\textwidth}{.5pt}}

A direct application of change of variable.s

{\bf (4.23)\rule{\textwidth}{.5pt}}

Skipping because I am lazy.

{\bf (4.24)\rule{\textwidth}{.5pt}}

REDO first part is MGF, but not sure how to do the second part.

{\bf (4.26)\rule{\textwidth}{.5pt}}

REDO didn't really understand how to do this one.

{\bf (4.27)\rule{\textwidth}{.5pt}}

REDO got lost in the algebra.

{\bf (4.30)\rule{\textwidth}{.5pt}}

I struggle with part (b) for some reason.

{\bf (4.31)\rule{\textwidth}{.5pt}}

I messed up part (c), but all of these are straight forward.

{\bf (4.33)\rule{\textwidth}{.5pt}}

TODO

{\bf (4.35)\rule{\textwidth}{.5pt}}

Direct application of the conditioning variance formula.

{\bf (4.39)\rule{\textwidth}{.5pt}}

REDO This is a really hard problem. I need to study more combinatorics to really tackle this.

{\bf (4.41)\rule{\textwidth}{.5pt}}

Since covariance is an inner product,
\begin{align*}
Cov(X, a)
&= \innerproduct{X - \mu}{a - \mu} \\
&= \innerproduct{X}{a - \mu} - \innerproduct{\mu}{a - \mu} \\
&= \overline{\innerproduct{a - \mu}{X}} - \overline{\innerproduct{a - \mu}{\mu}} \\
&= \innerproduct{X}{a}  - \innerproduct{X}{\mu} - \innerproduct{\mu}{a} + \innerproduct{\mu}{\mu} \\
&= \mu a - \mu^2 - \mu a + \mu^2 \\
&= 0.
\end{align*}

{\bf (4.45)\rule{\textwidth}{.5pt}}

Ugh, I skipped this because it was so long.

{\bf (4.47)\rule{\textwidth}{.5pt}}

REDO typical counter example is tricky tricky.

{\bf (4.51)\rule{\textwidth}{.5pt}}

Yeah, my answers have issues at 0. I am not sure how to remedy this.

{\bf (4.53)\rule{\textwidth}{.5pt}}

REDO really cool problem. I totally messed it up.

{\bf (4.55)\rule{\textwidth}{.5pt}}

Pretty straight forward actually.

{\bf (4.64)\rule{\textwidth}{.5pt}}

(a), (b) follow from Schwartz inequality and the linearity of integration.

\section*{Notes}

8 / 24
\rule{\textwidth}{.5pt}

8 / 25
\rule{\textwidth}{.5pt}


\end{document}
